Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-06-04 report/report.tex
Add source for virtual city image

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_virtual_city}
    \caption{Real-world cities are complex collections of buildings, blocks and road networks that interconnect them all. Creating 3D virtual cities using methods of procedual generation is an emerging research field that comes with its own set of challenges. This project deals with generating virtual cities from OpenStreetMap data, and the technical challenges therein.}
    \label{fig:virtual-city}
\end{figure}

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{img_virtual_city}
    \caption{Real-world cities are complex collections of buildings, blocks and road networks that interconnect them all. Creating 3D virtual cities using methods of procedual generation is an emerging research field that comes with its own set of challenges. This project deals with generating virtual cities from OpenStreetMap data, and the technical challenges therein.$^0$}
    \label{fig:virtual-city}
\end{figure}

\footnotetext{Image source: Downtown Boston 3D City Model in Infraworks 360, available via: https://gallery.autodesk.com/civilinfrastructure/projects/490/downtown-boston-3d-city-model-in-infraworks-360}
